Caribou Demographic Projection - interesting & informative title TBD

### 2022-12-15 analysis/paper/paper.Rmd
setting up to knit on Anna's machine

#set paths
data_path_raw <- "analysis/data/raw_data/"
data_path_drvd <- "analysis/data/derived_data"
app_path <- "C:/Users/HughesJo/Documents/gitprojects/BayesianCaribouDemographicProjection"

>>>>

#set paths
data_path_raw <- "analysis/data/raw_data/"
data_path_drvd <- "analysis/data/derived_data"

cd <- here::here()
app_path <- gsub("Caribou-Demographic-Projection-Paper","BayesianCaribouDemographicProjection",cd,fixed=T)
